%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Samuel Norling} \\ \vspace{1pt}
    \small 612-839-3342 $|$ \href{mailto:sanorling12321@gmail.com}{\underline{sanorling12321@gmail.com}} $|$ 
    \href{https://linkedin.com/in/x}{\underline{linkedin.com/in/SamuelNorling}} $|$
    \href{https://github.com/x}{\underline{github.com/SaNorling}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Belmont University}{Nashville, TN}
      {Bachelor of Science in Computer Science minor in music}{May 2024}
          \resumeItemListStart
            \resumeItem{Operating Systems}   
            \resumeItem{Computer Organization}
            \resumeItem{Human Computer Interaction (UI/UX course)}
            \resumeItem{Programming Languages}
            \resumeItem{Data Structures \& Algorithms}
            \resumeItem{Programming 1 \& 2}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intern - Software Development}{September 2024 - December 2024}
      {Reaching a Generation}{South Africa}
      \resumeItemListStart
        \resumeItem{Contributed to the development of an Enterprise Resource Planning (ERP) system to automate high-frequency organizational tasks.}
        \resumeItem{Frontend Development: Designed authentication pages (login, signup, password reset) and dynamic dashboards integrating tables, icons, and calendars. Developed additional functional pages for employee management and event scheduling.}
        \resumeItem{Quickly learned and applied technologies including HTML, CSS, Bootstrap, Tailwind CSS, and JavaScript, delivering functional pages within tight deadlines.}
        \resumeItem{Showcased strong UI/UX design principles, mastering advanced CSS techniques like FLEXbox and Grid layouts}
      \resumeItemListEnd
      
    \resumeSubheading
      {Electronics Advisor}{2022 - 2024}
      {Best Buy,}{Nashville, TN}
      \resumeItemListStart
        \resumeItem{Provide expert advice on electronics, ensuring customers make informed purchasing decisions.}
        \resumeItem{Train new hires on product knowledge and customer service best practices.}
      \resumeItemListEnd
      
     
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ERP System Development (Internship)} $|$ \emph{Technologies used}}{}
          \resumeItemListStart
            \resumeItem{Delivered user-friendly interfaces and backend components, automating organizational processes and increasing efficiency.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Dynamic Dashboards} $|$ \emph{Technologies used}}{}
          \resumeItemListStart
            \resumeItem{Designed visually appealing, interactive dashboards using JavaScript, Bootstrap, and Django.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Calculators and Weather Converters} $|$ \emph{Technologies used}}{}
          \resumeItemListStart
            \resumeItem{Built functional applications in Python, C++, Java, and Swift, enhancing programming and debugging expertise.}
          \resumeItemListEnd  

      \resumeProjectHeading
          {\textbf{Small Games Development} $|$ \emph{Technologies used}}{}
          \resumeItemListStart
            \resumeItem{Created engaging mini-games across multiple programming languages, blending creativity with technical proficiency.}
          \resumeItemListEnd         

    \resumeSubHeadingListEnd


%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, C\#, Java, JavaScript, SQL, Swift, HTML, CSS, PowerShell} \\
     \textbf{Frameworks}{: Django, Bootstrap, Tailwind CSS, FLEXbox, CSS Grid, Git} \\
     \textbf{Soft Skills}{: Effective communication, rapid learning agility, problem-solving, strong work ethic}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
